---
title: "Statistical Inference project 2"
author: "Madan Lamichhane"
date: "December 27, 2015"
output: pdf_document
---
## Project description
The goal of the project is to analyze tooth growth using R package and study basic expoloratry data analysis.

## Load Data and Data Summary 
```{r}
data(ToothGrowth)
str(ToothGrowth)
```

## Visual Analysis

```{r}
library(ggplot2)
avg <- aggregate(len~.,data=ToothGrowth,mean)
g <- ggplot(aes(x=dose, y = len), data = ToothGrowth) + 
geom_point(aes(color = supp)) 
g <- g + geom_line(data=avg,aes(group=supp,colour=supp))
print(g)
```

```{r}
ggplot(aes(x = factor(dose), y = len), data = ToothGrowth) + 
geom_boxplot(aes(fill = factor(dose)))
```

## Tooth length and delivary method

```{r}
ggplot(aes(x = supp, y = len), data = ToothGrowth) + 
geom_boxplot(aes(fill = supp))
```

## Relation between delivary methods
```{r}
ggplot(aes(x = supp, y = len), data = ToothGrowth) +
geom_boxplot(aes(fill = supp)) + facet_wrap(~ dose)
```

## Hypothesis testing

```{r}
dose1 <- subset(ToothGrowth, dose %in% c(0.5, 1.0))
dose2 <- subset(ToothGrowth, dose %in% c(0.5, 2.0))
dose3 <- subset(ToothGrowth, dose %in% c(1.0, 2.0))
t.test(len ~ dose, paired = F, var.equal = F, data = dose1)
```

```{r}
 t.test(len ~ dose, paired = F, var.equal = F, data = dose2)
```

```{r}
t.test(len ~ dose, paired = F, var.equal = F, data = dose3)
```

## Supplement as a factor
```{r}
t.test(len ~ supp, paired = F, var.equal = F, data = ToothGrowth)
```

## Conclusion
From this study we can conclude that the supplement type does not have effect on tooth growth and increasing dose levels leads to increased tooth growth.




