---
title: "Statistical Inference Project 1"
author: "Madan Lamichhane"
date: "December 27, 2015"
output: pdf_document
---

## Project Description
This project investigate the exponential distribution in R and compare with the central Limit Theorem. The exponential distribution has been simulated using rexp(n, lambda) where lambda is a rate paramenter which has been set to 0.2. This investigation has been performed over 40 exponentials. 

## Simulation
We can perform simulation over the 40 exponential suing fowllowing r codes.

```{r}
set.seed(1)
lambda = 0.2
numSim = 1000
sampleSize = 40
sim = matrix(rexp(numSim * sampleSize, rate=lambda), numSim, sampleSize)
simMean = rowMeans(sim)
```

The simulation data can be plotted as


```{r, echo=FALSE}
hist(simMean, col="red", main="Histogram of Simulation Mean", xlab="Simulation means")
```

## Comparision of mean

The sample and theoretical mean can be evaluated using following r-codes.

```{r}
meanData = mean(simMean)
theoMean = 1/lambda
```

```{r}
meanData
theoMean
```
The mean from simulation is  4.990025 whereas the theoretical mean is 5.0.

## Comparision of varaince

Similarly the variance from the simulation can be compared from the theoretical variance using following codes

```{r}
simVar = var(simMean)
theoVar = (1/lambda)^2/sampleSize
```
```{r}
simVar 
theoVar
```
The varainace obtained from the simulation is  0.6177072 nearly equal to theoretical varaince 0.625.

## Approximating with normal distribuation
```{r, message=FALSE}
library(ggplot2)
pData <- data.frame(simMean);
a <- ggplot(pData, aes(x =simMean))
a <- a + geom_histogram(aes(y=..density..), colour="black",
fill = "red")
a + geom_density(colour="green", size=1);
```

## Matching confidence interval
```{r}
simConInterval = round(mean(simMean) + c(-1,1)*1.96*sd(simMean)/sqrt(sampleSize), 3)
theoConInterval = theoMean + c(-1, 1) * 1.96 * sqrt(theoVar)/sqrt(sampleSize);
```

```{r}
simConInterval
theoConInterval
```

```{r}
qqnorm(simMean);
qqline(simMean)
```
